% !TeX TXS-program:compile = txs:///pdflatex

\documentclass[11pt,a4paper]{ltxdoc}
\usepackage{crimson}
\renewcommand*\ttdefault{cmvtt}
\usepackage[T1]{fontenc}
\usepackage{cabin}
\usepackage{vectorlogos}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{tabularray}
\usepackage{fontawesome5}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lfoot{\sffamily\small [vectorlogos]}
\cfoot{\sffamily\small - \thepage{} -}
\rfoot{\hyperlink{matoc}{\small\faArrowAltCircleUp[regular]}}
\usepackage{hologo}
\providecommand\tikzlogo{Ti\textit{k}Z}
\providecommand\TeXLive{\TeX{}Live\xspace}
\providecommand\PSTricks{\textsf{PSTricks}\xspace}
\let\pstricks\PSTricks
\let\TikZ\tikzlogo

\usepackage{hyperref}
\urlstyle{same}
\hypersetup{pdfborder=0 0 0}
\usepackage[margin=2cm]{geometry}
\setlength{\parindent}{0pt}
\def\TPversion{0.1.2}
\def\TPdate{29/11/2023}
\usepackage{tcolorbox}
\tcbuselibrary{skins,hooks,listingsutf8}
\usepackage{soul}
\sethlcolor{lightgray!25}
\NewDocumentCommand\MontreCode{ m }{%
	\hl{\vphantom{\texttt{pf}}\texttt{#1}}%
}

\begin{document}

\pagestyle{fancy}

\thispagestyle{empty}

\begin{center}
	\begin{minipage}{0.88\linewidth}
	\begin{tcolorbox}[colframe=yellow,colback=yellow!15]
		\begin{center}
			\begin{tabular}{c}
				{\Huge \texttt{vectorlogos}}\\
				\\
				{\LARGE Insert, 'inline', vectorial,} \\
				{\LARGE logos of 'classic' softwares.} \\
				\\
				{\small \texttt{Version \TPversion{} -- \TPdate}}
		\end{tabular}
		\end{center}
	\end{tcolorbox}
\end{minipage}
\end{center}

\begin{center}
	\begin{tabular}{c}
	\texttt{Cédric Pierquet}\\
	{\ttfamily c pierquet -- at -- outlook . fr}\\
	\texttt{\url{https://github.com/cpierquet/vectorlogos}} \\
\end{tabular}
\end{center}

\hrule

\vfill

\begin{tcolorbox}[colframe=lightgray,colback=lightgray!5]
\begin{center}
\scalebox{4}[4]{\logogeogebra}\hspace{1cm}\scalebox{4}[4]{\logogeogebra[icon]}

\medskip

\scalebox{4}[4]{\logoscratch}\hspace{1cm}\scalebox{4}[4]{\logoscratch[alt]}\hspace{1cm}\scalebox{4}[4]{\logoscratch[cat]}

\medskip

\scalebox{4}[4]{\logotexstudio}

\medskip

\scalebox{4}[4]{\logoemacs}\hspace{1cm}\scalebox{4}[4]{\logoemacs[alt]}

\medskip

\scalebox{4}[4]{\logotexmaker}\hspace{1cm}\scalebox{4}[4]{\logotexmaker[alt]}
\end{center}
\end{tcolorbox}

\vfill~

\hrule

\medskip

\emph{%
Logos came with GNU GPL or CC BY-SA (3.0 or 4.0).\\
Some brand icons/logos are trademarks of their respective owners. Please do not use brand icons/logos for any purpose except to represent the company, product, or service to which they refer.%\\
%"Python" and the Python Logo are trademarks of the Python Software Foundation (\url{https://www.python.org/psf/trademarks/}).%
}

\medskip

\hrule

\vspace*{5mm}

\pagebreak

\phantomsection

\hypertarget{matoc}{}

\tableofcontents

\vspace*{5mm}

%\hrule

\pagebreak

\section{Introduction}

\subsection{Description, loading}

With this package you can insert inline (vectorial) logos of 'classic' softwares.

The format of the logos is \textsf{pdf}, from \textsf{svg} files (given by \textsf{GNU GPL} or \textsf{CC-BY-3.0 / CC-BY-4.0} ot \textsf{MIT} licenses).

\medskip

Each logo can be integrated within a classic \MontreCode{\textbackslash includegraphics} command.

The package provides macros to insert them \textit{inline}, with automatic height and alignment.

\medskip

To load the package, simply use :

\begin{quote}
\begin{verbatim}
\usepackage{vectorlogos}
\end{verbatim}
\end{quote}

\subsection{Available logos, by name, for manual insertion}

Available logos are :

\medskip

\begin{tblr}{width=\linewidth,colspec={Q[m,l]Q[l,m]X[m,l]},cells={font=\LARGE\ttfamily,bg=teal!5},column{1}={font=\LARGE\bfseries\sffamily}}
	\hline
	emacs 		& vectorlogo-emacs.pdf 			& \logoemacs\ 			\\
				& vectorlogo-emacs-alt.pdf		& \logoemacs[alt]		\\
	\hline
	geogebra	& vectorlogo-geogebra.pdf 		& \logogeogebra\		\\
				& vectorlogo-geogebra-icon.pdf	& \logogeogebra[icon]	\\
	\hline
	scratch		& vectorlogo-scratch.pdf 			& \logoscratch\			\\
				& vectorlogo-scratch-alt.pdf		& \logoscratch[alt]	\\
				& vectorlogo-scratch-cat.pdf		& \logoscratch[cat]	\\
	\hline
	texmaker	& vectorlogo-texmaker.pdf			& \logotexmaker\		\\
				& vectorlogo-texmaker-alt.pdf		& \logotexmaker[alt]	\\
	\hline
	texstudio	& vectorlogo-texstudio.pdf			& \logotexstudio\		\\
\end{tblr}

\pagebreak

\section{The macros}

\subsection{A simple generic macro}

In order to insert an \textit{existing} vectorial logo, simpy use :

\begin{quote}
\begin{verbatim}
\simplevectorlogo*[options includegraphics]{name}
\end{verbatim}
\end{quote}

There's no automatic height or raising, it's just an \textit{alias} of a classic \MontreCode{\textbackslash includegraphics} with the given names of the precedent tabular.

\begin{tcblisting}{}
\simplevectorlogo*[height=1.5cm]{scratch}\par
\simplevectorlogo*[height=4cm]{scratch-cat}\par
\simplevectorlogo*[scale=0.33]{texstudio}\par
\simplevectorlogo*{emacs}\par
\simplevectorlogo*[width=3cm]{geogebra-icon}
\end{tcblisting}

\pagebreak

\subsection{A generic inline macro}

In order to insert a vectorial logo inline, simpy use :

\begin{quote}
\begin{verbatim}
\vectorlogo[option]{name}
\end{verbatim}
\end{quote}

The height (automatically calculated) of the logo is given by :

\begin{itemize}
	\item 90\,\% of the box \fbox{abcd...xyzABCD...XYZ} in the current font ;
	\item raised 5\,\% bottom of the depth of \fbox{q} in the current font.
\end{itemize}

Available \textsf{names} are :

\begin{multicols}{3}
	\begin{itemize}
		\item \texttt{emacs}
		\item \texttt{geogebra}
		\item \texttt{scratch}
		\item \texttt{texmaker}
		\item \texttt{texstudio}
	\end{itemize}
\end{multicols}

Available \textsf{options} are given by the suffix of alt logos.

\begin{tcblisting}{}
%other font and other size
{\Large\sffamily For example, it's a vectorial logo \vectorlogo[icon]{geogebra} with inline insertion.}
\end{tcblisting}

\begin{tcblisting}{}
%other font and other size
\scalebox{3.25}[3.25]{\ttfamily The cat \vectorlogo[cat]{scratch} logo, inline !}
\end{tcblisting}

\subsection{Special commands}

There's an other (shortcut) way to insert logos, with a shortcut-name, like in \textsf{fontawesome5} :
%\logopython[option]

\begin{quote}
\begin{verbatim}
\logoscratch[option]
\logogeogebra[option]
\logotexstudio[option]
\logoemacs[option]
\logotexmaker[option]
\end{verbatim}
\end{quote}

Available options are given by the suffix of alt logos.

\begin{tcblisting}{}
A sample logo, \logoemacs[alt], inline.
\end{tcblisting}

\pagebreak

\section{Samples and personal logos}

\subsection{Samples}

\begin{tcblisting}{listing only}
%useful macro
\newcommand\samplevectorlogo[1]{{\LARGE Inline {#1} logo}\par}
\end{tcblisting}

\newcommand\samplevectorlogo[1]{{\LARGE Inline {#1} logo}\par}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logogeogebra}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logogeogebra[icon]}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logoscratch}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logoscratch[alt]}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logoscratch[cat]}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logotexstudio}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logoemacs}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logoemacs[alt]}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logotexmaker}
\end{tcblisting}

\begin{tcblisting}{listing side text}
\samplevectorlogo{\logotexmaker[alt]}
\end{tcblisting}

\pagebreak

\subsection{Personal logos}

If you wan't to use, \textit{inline}, your personal logos (located in workdir or in a \textsf{texmf} folder), you can use the command :

\begin{quote}
\begin{verbatim}
\simplevectorlogo[scale]{filename}
\end{verbatim}
\end{quote}

\MontreCode{[scale]}, which is \MontreCode{0.9} by default, is the ratio between the height of the logo and the height of the current 'text'.

\MontreCode{filename} is the fullname of the logo.

\begin{tcblisting}{}
{\Huge A perfect test \simplevectorlogo{example-image-16x10.pdf} inline.}
\end{tcblisting}

\begin{tcblisting}{}
{\Huge A perfect test \simplevectorlogo[1]{example-image-16x10.pdf} inline.}
\end{tcblisting}

\begin{tcblisting}{}
{\LARGE Another perfect test \simplevectorlogo[0.5]{example-image-16x10.pdf} inline.}
\end{tcblisting}

\begin{tcblisting}{}
{\LARGE Another perfect test \simplevectorlogo[2]{example-image-16x10.pdf} inline.}
\end{tcblisting}

\vfill~

\section{History}

\begin{quote}
\begin{verbatim}
0.1.2 : Alt command for manual insertion, with existing img
0.1.1 : Update licenses
0.1.0 : Initial version
\end{verbatim}
\end{quote}

\end{document}